---
title: "Autoregressive RDM"
author: "Sven Wientjes"
format: gfm
editor: visual
---

In this document, we will discuss, fit, and evaluate the Racing Diffusion Model (RDM) using Stan. Of special interest is whether we can make the parameters of the RDM fluctuate according to an AR(1) process. For a tutorial on how to do this with the DDM, check [this document](https://github.com/SvenWientjes/AR1_DDM) instead. It is recommended to scroll through that tutorial first, because some of the concepts introduced there are assumed prior knowledge for following this tutorial.

## The Racing Diffusion Model (RDM)

The RDM is a generative model of responses and response times. Typically, it has one racing accumulator for each possible response option. These accumulators evolve according to an inverse Gaussian or Wald distribution: For an observed response time $t$, defining $y = t - T_{er}$ (with $T_{er}$ being a "non-decision time") and assuming a fixed diffusion noise $s = 1$ (an assumption we will later relax) this gives probability density function $p(y|v,b) = \frac{b}{\sqrt{2 \pi y^3}}e{-\frac{(b-vy)^2}{2y}}$ and cumulative density $P(y|v,b) = \Phi(\frac{vy-b}{\sqrt{y}})+e^{2bv} \cdot \Phi(\frac{-vy-b}{\sqrt(y)})$. Here, $v$ is a drift rate and $b$ is a boundary.

We can use these density functions to represent the decision process as a competition between multiple responses. Biases in favor of a particular response can be incorporated as a parameter $db$. Each accumulator can have its own diffusion noise $s$, but at least one must be fixed to 1 to satisfy scaling constraints. When this noise differs across accumulators, drift rates and boundaries can be rescaled by dividing by the respective diffusion noise, allowing likelihoods to be computed as usual. The likelihood of observing response $i$ at time $t$ is then given by the density of accumulator $i$ reaching threshold at time $t$ multiplied by the cumulative probability that all other accumulators have not reached threshold before $t$:

$f_i(y|\mathbf{v}, b, \mathbf{db}, \mathbf{s}) = p(y|\frac{v_i}{s_i}, \frac{b-db_i}{s_i}) \prod_{j \neq i}[1 - P(y|\frac{v_j}{s_j}, \frac{b-db_j}{s_j})]$

### A 2-AFC parameterization

In a 2-alternative forced choice task, we can set up a particularly effective parameterization in terms of the differences between the two relevant accumulators. The diffusion process is going to be biased based on response identity, but the drifting process itself (both its mean $v$ and its variance $s$) are going to be determined by the stimulus determining which of the two racers corresponds to the correct response.

In total, our 2AFC RDM will have 6 free parameters, $[B, db, V, vd, sd, T_{er}]$. $B$ corresponds to the overall response threshold, $db$ corresponds to the bias in favor of a particular racer (negative values will favor response 1, positive values will favor response 2). $V$ is the average drift rate between the two racers. $vd$ and $sd$ are the difference in drift rate and drift rate variability respectively, between the racer corresponding to the currently correct response and the racer corresponding to the currently incorrect response. $T_{er}$ is a non-decision time.

Note that the parameters of this model do not vary across trials, yet we have six free parameters. This is two more than the DDM without between-trial variability. This is because the RDM incorporates two mechanisms in the generative process that the DDM does not. The DDM does not contain an "average drift rate" analogous to $V$--instead there is only a single drifting state that evolves according to the relative evidence in favor of a particular option, mostly resembling $vd$. Also, in the DDM, by nature of there being only a single drifting state, there can be no difference in variability analogous to $sd$ in the RDM.

## Exploring data

Lets begin by loading some packages and useful functions:

```{r}
#| warning: false
#| message: false
library(cmdstanr)
library(data.table)
library(ggplot2)
source("functions/CAF.R")
source("functions/correlated_errors.R")
source("functions/rWald.R")
```

Before we fit the RDM and discuss its autoregressive extension, lets explore some empirical data we would like to explain. We will use Experiment 2B from [Desender et al. (2022)](https://doi.org/10.1038/s41467-022-31727-0). Let's load it and do some simple data wrangling:

```{r}

# Load data
MyData <- fread("https://raw.githubusercontent.com/kdesende/dynamic_influences_on_static_measures/refs/heads/main/data_exp2B.csv")

# Get nicer participant numbers
MyData$pp         <- ordered(MyData$sub)
levels(MyData$pp) <- c(1:99)

# Recode stimulus and response to 1/2
MyData[stim==1,stim:=2]
MyData[stim==0,stim:=1]
MyData[response==1,response:=2]
MyData[response==0,response:=1]

# Mark trials for exclusion
MyData$yi <- 1
MyData[rt<0.1|rt>3.0,yi:=0]
```

Note that we use `$yi` to mark fast and slow outliers with a 0, while all other trials are marked with a 1. This is how we deal with data exclusion, while maintaining the original temporal structure of the data.

### Visualizing RT distributions

We can visualize two marginal RT distributions for illustration purposes:

```{r}
ggplot() +
  geom_density(data = MyData[pp==69 & yi==1], linetype="dashed",linewidth=1, aes(x=rt), color="orange") +
  geom_density(data = MyData[pp==15 & yi==1], linetype="dashed",linewidth=1, aes(x=rt), color="purple") +
  theme_minimal()
```

### Visualizing the conditional accuracy function (CAF)

The Conditional Accuracy Function (CAF) partitions this response time distribution into different regions with equal numbers of trials in them. It then visualizes the proportion of correct trials in each bin against the mean RT of the trials in that bin. This reveals substantially more errors for very fast responses, as well as substantially more errors for very slow responses.

```{r}
# Get CAF and confidence interval
CAF <- calculate_group_caf(MyData[yi==1], "rt", "cor", "pp", num_bins=7)
CAF[,min_acc:=mean_acc-1.96*se_acc]
CAF[,max_acc:=mean_acc+1.96*se_acc]

## Group conditional accuracy function
ggplot(CAF, aes(x=mean_rt, y=mean_acc)) +
  geom_point() +
  geom_errorbar(aes(ymin=min_acc,ymax=max_acc),width=0.05) +
  geom_line() +
  theme_minimal() +
  xlab("RT") + ylab("Accuracy")
```

## Fitting and exploring the RDM

We can fit the RDM by running the code below. Note that this may take some time and compute. If you do not find it necessary to spend these resources, download my fits here and unpack the `.csv` files into `fits/RDM`.

```{r}
#| eval: false

# Load model
RDMmod <- cmdstan_model("models/RDM.stan")

# Run over participants to fit
for(PNUM in 1:99){
  Pdat <- MyData[pp==PNUM]
  
  DataList <- list(N       = nrow(Pdat),
                   choice  = Pdat$response,
                   stim    = Pdat$stim,
                   y       = Pdat$rt,
                   yi      = Pdat$yi,
                   min_rt  = min(Pdat[yi==1]$rt))
  
  # Fit the model
  fit <- RDMmod$sample( #65s, 0d
    data            = DataList,
    chains          = 4,
    parallel_chains = 4,
    adapt_delta     = 0.80,
    max_treedepth   = 10,
    init_buffer     = 200,
    term_buffer     = 200,
    window          = 25,
    iter_warmup     = 1975,
    iter_sampling   = 2000,
    output_dir      = "fits/RDM",
    output_basename = paste0("RDM_pp",formatC(PNUM,width=2,flag="0"))
  )
}

```

### Simulating from the RDM

Stan gives us the parameters of the RDM, but we are interested in how well the RDM accounts for our data. Therefore, we need to simulate from the model, using the parameters we got from Stan. The code below runs these simulations. It is a bit inefficiently programmed, but works robustly. Again, you could instead download my simulations here and unpack them as `simulations/RDM_simulations.csv`.

```{r}
#| eval: false

# Sample from every participant
N_sims       <- 500
total_sims   <- N_sims * 500
SIM_list     <- list()
downsamp_idx <- round(seq(1,8000,length.out=N_sims))
for(PNUM in 1:99){
  print(paste0("=================================="))
  print(paste0("Simulating participant ",PNUM,"/99"))
  
  # Get participant data and fit
  Pdat   <- MyData[pp==PNUM]
  RDMfit <- as_cmdstan_fit(paste0("fits/RDM/RDM_pp",formatC(PNUM,width=2,flag="0"),"-",1:4,".csv"))
  
  # Get parameters over time
  v1_stim1 <- RDMfit$draws("v_pos1_s[1]",format="matrix")[downsamp_idx,]
  b1_stim1 <- RDMfit$draws("b_pos1_s[1]",format="matrix")[downsamp_idx,]
  v2_stim1 <- RDMfit$draws("v_min1_s[1]",format="matrix")[downsamp_idx,]
  b2_stim1 <- RDMfit$draws("b_min1_s[1]",format="matrix")[downsamp_idx,]
  
  v1_stim2 <- RDMfit$draws("v_pos1_s[2]",format="matrix")[downsamp_idx,]
  b1_stim2 <- RDMfit$draws("b_pos1_s[2]",format="matrix")[downsamp_idx,]
  v2_stim2 <- RDMfit$draws("v_min1_s[2]",format="matrix")[downsamp_idx,]
  b2_stim2 <- RDMfit$draws("b_min1_s[2]",format="matrix")[downsamp_idx,]
  
  t0 <- RDMfit$draws("t0",format="matrix")[downsamp_idx,]
  
  # Get simulated choice/RTs
  sim_rt     <- numeric(total_sims)
  sim_choice <- numeric(total_sims)
  was_stim   <- numeric(total_sims)
  
  si <- 1
  for(s in 1:N_sims){
    print(paste0("    Simulating sample ",s,"/",dim(v1_stim1)[1]))
    for(t in 1:nrow(Pdat)){
      if(Pdat[t,stim]==1){
        racers <- rWald(n = 2, 
                        B = c(b1_stim1[s],b2_stim1[s]), 
                        v = c(v1_stim1[s],v2_stim1[s]), 
                        A = 0)
      }else if(Pdat[t,stim]==2){
        racers <- rWald(n = 2, 
                        B = c(b1_stim2[s],b2_stim2[s]), 
                        v = c(v1_stim2[s],v2_stim2[s]), 
                        A = 0)
      }
      sim_rt[si]     <- min(racers) + t0[s]
      sim_choice[si] <- which.min(racers)
      was_stim[si]   <- Pdat[t,stim]
      si             <- si+1
    }
  }
  SIM_list[[PNUM]] <- data.table(
    p        = PNUM,
    sim      = rep(1:N_sims, each = nrow(Pdat)),
    t        = rep(1:nrow(Pdat), N_sims),
    rt       = sim_rt,
    choice   = sim_choice,
    was_stim = was_stim,
    correct  = sim_choice==was_stim
  )
}
SIM <- rbindlist(SIM_list)
fwrite(SIM, "simulations/RDM_simulations.csv.gz", compress = "gzip", compressLevel = 9)
```

### Posterior predictive check of RT distributions

We can now check how well our simulations match the empirical RT distributions of the two participants we visualized above:

```{r}

# Load simulations
SIM <- fread("simulations/RDM_simulations.csv.gz")

# Make density plot
ggplot() +
  geom_density(data = MyData[pp==69 & yi==1], linetype="dashed",linewidth=1, aes(x=rt), color="orange") +
  geom_density(data = MyData[pp==15 & yi==1], linetype="dashed",linewidth=1, aes(x=rt), color="purple") +
  geom_density(data = SIM[p==69&rt>0.1&rt<3.0], linewidth=0.5, aes(x=rt), color="orange") +
  geom_density(data = SIM[p==15&rt>0.1&rt<3.0], linewidth=0.5, aes(x=rt), color="purple") +
  theme_minimal()
```

Compared to the fits with the (AR1) DDM ([see here](github.com/SvenWientjes/AR1_DDM)) we obtain much better fits to the marginal RT distributions.

### Posterior predictive check of the CAF

We can also check what the relationship between response times and errors is according to this model:

```{r}
#| cache: true
#| warning: false
#| message: false

# Get simulated CAF
CAFlist <- list()
for(simje in 1:SIM[,max(sim)]){
  CAFlist[[simje]] <- calculate_group_caf(SIM[sim==simje&rt>0.1&rt<3.0], "rt", "correct", "p", num_bins=7)
}
CAF_sim <- rbindlist(CAFlist)

# Compute intervals
CAF_ppc <- CAF_sim[,list(min_rt = bayestestR::hdi(mean_rt)$CI_low,
                         max_rt = bayestestR::hdi(mean_rt)$CI_high,
                         med_rt = median(mean_rt),
                         min_ac = bayestestR::hdi(mean_acc)$CI_low,
                         max_ac = bayestestR::hdi(mean_acc)$CI_high,
                         med_ac = median(mean_acc)),
                   by=rt_bin]

# Visualize
ggplot() +
  geom_point(data=CAF,aes(x=mean_rt,y=mean_acc)) +
  geom_errorbar(data=CAF,aes(x=mean_rt,y=mean_acc,ymin=min_acc,ymax=max_acc),width=0.05) +
  geom_line(data=CAF,aes(x=mean_rt,y=mean_acc)) +
  geom_line(data=CAF_ppc, aes(x=med_rt,y=med_ac),linetype="dashed") +
  geom_errorbar(data=CAF_ppc, aes(x=med_rt,ymin=min_ac,ymax=max_ac),linetype="dashed") + 
  geom_errorbarh(data=CAF_ppc, aes(xmin=min_rt,xmax=max_rt,y=med_ac),linetype="dashed") +
  theme_minimal() +
  xlab("RT") + ylab("Accuracy")

# Remove large files for caching
rm(CAFlist, CAF_sim, CAF_ppc)
```

Here, the solid lines correspond to the empirical CAF and the dashed lines correspond to the posterior predicted CAF from the RDM. We can see that the RDM tends to have a decreasing CAF. This is because as the decision process takes longer, the probability of the incorrect (on average slower) racer winning increases. This happens in the RDM because the racers are not in competition. By contrast, in the DDM, there is *strong competition*, because each piece of evidence in favor of one option counts as a piece of evidence against the other option. This tug-of-war leads to a flatter CAF for the DDM.

Now we see that the RDM provides better overall marginal fits to the RT distributions, but does not provide quite the right CAF. The next question to ask is whether between-trial fluctuations can help improve the fit to the CAF.

## Fitting and exploring the AR1-RDM model

To fit the parameters of the RDM as AR(1) processes, we can rely on the same trick as we did for the DDM. Interestingly, now we have an additional parameter that we can let fluctuate. We will fluctuate parameters $[B,db,V,db]$. In principle, diffusion-noise related parameters could also be made to fluctuate.

### Fitting the AR1-RDM model with Stan

We can fit the AR1-RDM model very similarly to how we fitted the regular RDM model. You can run this code, or download my simulations here.

```{r}
#| eval: false

# Load model
RDMmod <- cmdstan_model("models/RDM_AR1.stan")

# Loop over participants to fit
for(PNUM in 1:99){
  Pdat <- MyData[pp==PNUM]
  
  DataList <- list(N       = nrow(Pdat),
                   choice  = Pdat$response,
                   stim    = Pdat$stim,
                   y       = Pdat$rt,
                   yi      = Pdat$yi,
                   min_rt  = min(Pdat[yi==1]$rt))
  
  # Fit the model
  fit <- RDMmod$sample( #250s, 0d
    data            = DataList,
    chains          = 4,
    parallel_chains = 4,
    adapt_delta     = 0.90,
    max_treedepth   = 10,
    init_buffer     = 200,
    term_buffer     = 200,
    window          = 25,
    iter_warmup     = 1975,
    iter_sampling   = 2000,
    output_dir      = "fits/RDM_AR1",
    output_basename = paste0("RDM_AR1_pp",formatC(PNUM,width=2,flag="0"))
  )
}
```

There are a couple of chains where the fit did not go well for me. Usually, I would weed these out manually and see if refitting them solves the issue, perhaps with a higher `adapt_delta`. For now, lets continue to see how the model performs.

### Exploring the fit

We can visualize the trajectory of the RDM parameters: for a particular participant, and overlay a smooth Loess fit (blue line) to visualize any subtle structural changes that may not be obvious from between-trial noise:

```{r}
#| cache: true
#| warning: false
#| message: false

# Select participant & load fit
PNUM <- 1
RDMfit <- as_cmdstan_fit(paste0("fits/RDM_AR1/RDM_AR1_pp",formatC(PNUM,width=2,flag="0"),"-",1:4,".csv"))

# Extract parameters and compute posterior means
B_draws  <- apply(RDMfit$draws("B_t",format="matrix"),2,mean)
b_draws  <- apply(RDMfit$draws("b_t",format="matrix"),2,mean)
V_draws  <- apply(RDMfit$draws("V_t",format="matrix"),2,mean)
v_draws  <- apply(RDMfit$draws("v_t",format="matrix"),2,mean)


# Combine into a single data.table for plotting
plot_draws <- data.table(t = rep(1:500,4),
                         p = rep(c("B","db","V","dv"),each=500),
                         y = c(B_draws,b_draws,V_draws,v_draws))

# Plot
ggplot(plot_draws, aes(x=t,y=y)) +
  facet_wrap(.~p,scales="free") +
  geom_line() +
  geom_smooth() +
  theme_minimal()

# Remove big objects from cache
rm(RDMfit,B_draws,b_draws,V_draws,v_draws,plot_draws)
```

We can see that this participant has a strong structural fluctuation for the overall response threshold $B$, and minor fluctuations for the response bias $b$ and overall drift rate $V$. Let's explore another participant:

```{r}
#| cache: true
#| warning: false
#| message: false

# Select participant & load fit
PNUM <- 2
RDMfit <- as_cmdstan_fit(paste0("fits/RDM_AR1/RDM_AR1_pp",formatC(PNUM,width=2,flag="0"),"-",1:4,".csv"))

# Extract parameters and compute posterior means
B_draws  <- apply(RDMfit$draws("B_t",format="matrix"),2,mean)
b_draws  <- apply(RDMfit$draws("b_t",format="matrix"),2,mean)
V_draws  <- apply(RDMfit$draws("V_t",format="matrix"),2,mean)
v_draws  <- apply(RDMfit$draws("v_t",format="matrix"),2,mean)


# Combine into a single data.table for plotting
plot_draws <- data.table(t = rep(1:500,4),
                         p = rep(c("B","db","V","dv"),each=500),
                         y = c(B_draws,b_draws,V_draws,v_draws))

# Plot
ggplot(plot_draws, aes(x=t,y=y)) +
  facet_wrap(.~p,scales="free") +
  geom_line() +
  geom_smooth() +
  theme_minimal()

# Remove big objects from cache
rm(RDMfit,B_draws,b_draws,V_draws,v_draws,plot_draws)
```

For this participant, we see highly autocorrelated changes in the overall drift rate $V$. This is noteworthy, as the DDM does not have a parameter that corresponds to $V$--its drift rate corresponds more to $dv$ which is the difference between correct and incorrect drift rate.

#### Simulating choice-RT data

In order to check how well the AR1-RDM model fits the RT distributions and the CAF of the empirical data, we can simulate from the AR1-RDM model, very similar to how we can simulate from the regular RDM model. You can run this code, or download my simulations here.

```{r}
#| eval: false

# Get simulation parameters
N_sims       <- 500
total_sims   <- N_sims * 500
SIM_list     <- list()
downsamp_idx <- round(seq(1,8000,length.out=N_sims))

# Loop over participants to simulate
for(PNUM in 1:99){
  print(paste0("=================================="))
  print(paste0("Simulating participant ",PNUM,"/99"))
  
  # Get participant data and fit
  Pdat   <- MyData[pp==PNUM]
  RDMfit <- as_cmdstan_fit(paste0("fits/RDM_AR1/RDM_AR1_pp",formatC(PNUM,width=2,flag="0"),"-",1:4,".csv"))
  
  # Get parameters over time
  vacc <- RDMfit$draws("v_acc",format="matrix")[downsamp_idx,]
  bacc <- RDMfit$draws("b_acc",format="matrix")[downsamp_idx,]

  # Select parameters for each racer
  v1 <- vacc[,grep("v_acc\\[\\d+,1\\]",colnames(vacc))]
  v2 <- vacc[,grep("v_acc\\[\\d+,2\\]",colnames(vacc))]
  b1 <- bacc[,grep("b_acc\\[\\d+,1\\]",colnames(bacc))]
  b2 <- bacc[,grep("b_acc\\[\\d+,2\\]",colnames(bacc))]
  
  # Get non-decision time
  t0 <- RDMfit$draws("t0",format="matrix")[downsamp_idx,]
  
  # Simulate racer times
  r1 <- rWald(n = N_sims * nrow(Pdat),
              B = c(b1),
              v = c(v1),
              A = 0)
  r2 <- rWald(n = N_sims * nrow(Pdat),
              B = c(b2),
              v = c(v2),
              A = 0)
  
  # Select fastest racer
  rts     <- apply(rbind(r1,r2),2,min)
  choices <- as.numeric(c(r1 < r2))
  choices[choices==0] <- 2
  rts <- rts + rep(t0,each=N_sims)
  
  SIM_list[[PNUM]] <- data.table(
    p        = PNUM,
    sim      = rep(1:N_sims, nrow(Pdat)),
    t        = rep(1:nrow(Pdat), each=N_sims),
    rt       = rts,
    choice   = choices,
    was_stim = rep(Pdat[,stim],each=N_sims)
  )
}
SIM <- rbindlist(SIM_list)
fwrite(SIM, "simulations/RDM_AR1_simulations.csv.gz", compress = "gzip", compressLevel = 9)

```

#### Posterior predictions of RT distributions

We can visualize the marginal RT distributions again, and see we somewhat improved for one of these example participants! (purple)

```{r}
# Load simulations
SIM <- fread("simulations/RDM_AR1_simulations.csv.gz")

# Make density plot
ggplot() +
  geom_density(data = MyData[pp==69 & yi==1], linetype="dashed",linewidth=1, aes(x=rt), color="orange") +
  geom_density(data = MyData[pp==15 & yi==1], linetype="dashed",linewidth=1, aes(x=rt), color="purple") +
  geom_density(data = SIM[p==69&rt>0.1&rt<3.0], linewidth=0.5, aes(x=rt), color="orange") +
  geom_density(data = SIM[p==15&rt>0.1&rt<3.0], linewidth=0.5, aes(x=rt), color="purple") +
  theme_minimal()
```

#### Posterior predictions of the CAF

Lets see if the AR(1) processes helped improve our CAF fit:

```{r}
#| cache: true
#| warning: false
#| message: false
#| 
# Get simulated CAF plot
CAFlist <- list()
for(simje in 1:SIM[,max(sim)]){
  CAFlist[[simje]] <- calculate_group_caf(SIM[sim==simje&rt>0.1&rt<3.0], "rt", "correct", "p", num_bins=7)
}
CAF_sim <- rbindlist(CAFlist)

# Compute intervals
CAF_ppc <- CAF_sim[,list(min_rt = bayestestR::hdi(mean_rt)$CI_low,
                         max_rt = bayestestR::hdi(mean_rt)$CI_high,
                         med_rt = median(mean_rt),
                         min_ac = bayestestR::hdi(mean_acc)$CI_low,
                         max_ac = bayestestR::hdi(mean_acc)$CI_high,
                         med_ac = median(mean_acc)),
                   by=rt_bin]

ggplot() +
  geom_point(data=CAF,aes(x=mean_rt,y=mean_acc)) +
  geom_errorbar(data=CAF,aes(x=mean_rt,y=mean_acc,ymin=min_acc,ymax=max_acc),width=0.05) +
  geom_line(data=CAF,aes(x=mean_rt,y=mean_acc)) +
  geom_line(data=CAF_ppc, aes(x=med_rt,y=med_ac),linetype="dashed") +
  geom_errorbar(data=CAF_ppc, aes(x=med_rt,ymin=min_ac,ymax=max_ac),linetype="dashed") + 
  geom_errorbarh(data=CAF_ppc, aes(xmin=min_rt,xmax=max_rt,y=med_ac),linetype="dashed") +
  theme_minimal() +
  xlab("RT") + ylab("Accuracy")

# Remove large files for caching
rm(CAFlist, CAF_sim, CAF_ppc)
```

This is good! We capture the same qualitative pattern of both fast and slow errors, although the pattern is somewhat attenuated in our posterior predictions.

### Modeling correlated error patterns

One key pattern of AR(1)-like fluctuataing dynamics, identified by Vloeberghs et al. (2026), is that error identities correlate over time. Fast errors are more likely followed by fast errors rather than slow errors, and errors of response 1 are more likely followed by errors of response 1 rather than of response 2. Here we visualize both the empirical and posterior-predicted relationship between successive errors:

```{r}

# Compute empirical correlated errors
group_stats <- get_error_cor(MyData)

# Get posterior predicted correlated errors
SIM[,cor:=correct]; SIM$yi <- 1; SIM[,pp:=p];
SIM[,stim:=was_stim]

# Run posterior simulations
ERlist <- list()
for(simje in 1:SIM[,max(sim)]){
  ERlist[[simje]] <- get_error_cor(SIM[sim==simje])
}
ER_sim <- rbindlist(ERlist)

# Aggregate over simulations
ER_ppc <- ER_sim[,list(mean_prob = mean(mean_prob),
                       low_prob  = bayestestR::hdi(mean_prob)$CI_low,
                       high_prob = bayestestR::hdi(mean_prob)$CI_high),
                 by=.(er_class,prev_er_class)]

## Plot empirical correlated errors
ggplot(group_stats, aes(x = er_class, y = mean_prob, fill = prev_er_class)) +
  geom_bar(
    stat     = "identity", 
    position = position_dodge(width = 0.9), 
    color    = "black", 
    lwd = 0.3
  ) +
  geom_errorbar(
    aes(ymin     = ci_lower, ymax = ci_upper),
    position = position_dodge(width = 0.9),
    width    = 0.25, # Width of the error bar caps
    color    = "grey30"
  ) +
  scale_fill_brewer(palette = "Set2", name = "Previous Error Class") +
  theme_minimal() +
  xlab("Error class") + ylab("Probability of previous error class") +
  theme(legend.position="top")

## plot posterior predicted correlated errors
ggplot(ER_ppc, aes(x = er_class, y = mean_prob, fill = prev_er_class)) +
  geom_bar(
    stat     = "identity", 
    position = position_dodge(width = 0.9), 
    color    = "black", 
    lwd = 0.3
  ) +
  geom_errorbar(
    aes(ymin     = low_prob, ymax = high_prob),
    position = position_dodge(width = 0.9),
    width    = 0.25, # Width of the error bar caps
    color    = "grey30"
  ) +
  scale_fill_brewer(palette = "Set2", name = "Previous Error Class") +
  theme_minimal() +
  xlab("Error class") + ylab("Probability of previous error class") +
  theme(legend.position="top")


```

We can see that the AR1-RDM is highly accurate in recapitulating the correlated error structure, much more so than the AR1-DDM was!

## Conclusion

The AR1-RDM can perform much better than the AR1-DDM it seems, although it does show some instability for some participants. Future work should check if divergent fits can be fixed by refitting, or if reduced models need to be fit for the participants where stable convergence failed.
